\cleardoublepage
\chapter{Acknowledgements}
\vspace*{1cm}
It is a pleasure for me to express my gratitude to the many people who have helped me or have been an important part of my life the last three and a half years.

First of all, I am grateful to my supervisor in Copenhagen, Kristine Kilså, for supporting me all the way from my Bachelor work to pursuing the PhD degree. Although circumstances hindered an explicit supervision during most of the PhD I am incredibly thankful for the time and responsibility you trusted me with all this time.

I am equally thankful to my supervisor at Chalmers, Bo Albinsson, for all of the supervision and for the encouragement to follow my own ideas. I have always been free to pursue the projects I had in mind yet still been guided in the right direction, and I am grateful for that.

Of all the important people involved in my thesis, I am particularly grateful to Marcus Wilhelmsson at Chalmers for the very close collaboration we have had. You have been the weekly contact and supervisor in almost all of my projects and I will always be thankful for that. Most of these projects could not have happened without you. I admire your skills and talents and I am very happy for the friendship we have build up during the years.

I am thankful to the previous group members in Copenhagen, Eduardo Della Pia, Jeppe Fock and Martin Rosenberg, for the good coffee breaks and discussions we have had. Thank you Søren, for working on my projects and for testing the software. Thank you Erling, for nice discussions and software testing.

A warm thanks goes to all of the nice people I have met at Chalmers, both previous and current members. I am grateful to you Anke Dierckx for being a friend and close collaborator. Jakob Woller for the friendship and the many table tennis matches  we fought at Chalmers. Also, thank you Jonas Hannestad for the time spent helping with time-resolved measurements and data conversion.

I am thankful to all of my co-authors, in particular Karl B, Francois and Anke for the work you have put into these projects. Thank you Jon Burns and Eugen Stulz at Southampton University for our fruitful collaboration.

I am thankful to the Herschlag lab at Stanford for inviting me in as a visiting researcher, in particular to Dan and Xuesong for our collaboration and to Rishi for the many great discussions. I had a truly rewarding stay that I would not have been without.

Finally, I am forever thankful to my wife Susan for all of your love and support, even when I have brought home work and I am mentally distracted or my working hours have exceeded the maximum healthy dose. Thanks to my wonderful son Sigurd for putting a huge smile on my face every single day. Jeg kunne ikke være mere lykkelig, end når jeg er sammen med jer.

\vspace*{3cm}
\begin{center}
%\rule{5cm}{0.2mm}\\
\emph{
Søren Preus\\
\vspace*{0.2 cm}
Copenhagen, Denmark, December 2012}
\end{center}
